### 2021-02-15 Chapter-1/Chapter-1.tex
init
update

Side channels are inevitable in modern computer systems as the sensitive
information may be leaked through many kinds of inadvertent behaviors, such as power,
electromagnetic radiation, and even
sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
Among them, software-based side channel attacks, such as cache attacks, memory page
attacks, and controlled-channel attacks, are especially common and have been
studied for
years~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}. These
attacks result from vulnerable software and shared hardware components.
By observing program outputs or hardware behaviors, attackers can infer program
execution flows that manipulate secrets and guess secrets such as encryption
keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.

\section{Side-channel}

\subsection{Attacks}

\subsection{Defense}

@@

>>>>

Side channels are inevitable in modern computer systems as the sensitive
information may be leaked through many kinds of inadvertent behaviors, such as power, electromagnetic radiation, and even
sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
Among them, address-based side channel attacks, such as cache attacks, memory page attacks, and controlled-channel attacks, are especially common and have been studied for years~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}. These
attacks result from vulnerable software and shared hardware components.
By observing program outputs or hardware behaviors, attackers can infer program
execution flows that manipulate secrets and guess secrets such as encryption
keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.

In this chapter, we first introduce two code patterns that can be exploited to retrieve sensitive information. After that, we discuss some common attacks and corresponding defense strategies. The limitations of existing work motivate the research in the dissertation. Finally, we summarize the contributions of the dissertation.

\section{Side-channel Attacks}
\begin{figure}[tbp]
\begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
int secret[32];
...
while(i>0){
    r = (r * r) % n;
    if(secret[--i] == 1)
        r = (r * x) % n;   
}
\end{lstlisting}
\caption{Secret-dependent control-flow transfers}
\label{fig:secret:cf}
\end{figure}

\begin{figure}[tbp]
\begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
static char FSb[256] = {...}
... 
uint32_t a = *RK++ ^ \ 
(FSb[(secret)) ^
(FSb[(secret >> 8)] << 8 ) ^
(FSb[(secret >>16)] << 16 ) ^
(FSb[(secret >>24)] << 24 );
...
\end{lstlisting}
\caption{Secret-dependent data accesses}
\label{fig:secret:da}
\end{figure}

\section{Current Defense}

@@

\section{Contribution}
